\simname 2.0 User's Guide

### 2008-11-06 doc/manual.tex
update documentation for new speculation code
git-svn-id: https://nocs.stanford.edu/cgi-bin/svn.cgi/booksim2.0/trunk@817 ce7aba0d-9f81-40a6-a495-cecae84b0515

\item[MECS] A topology based on ***. Currently it only support 1 flit per packet.

@@

@@

\item[sw\_alloc\_arb\_type] The type of arbiter to use if a separable input- or output-first allocator is used for switch allocation.

@@

\item[vc\_alloc\_arb\_type] The type of arbiter to use if a separable input- or output-first allocator is used for virtual channel allocation.

@@

\subsubsection{The NoC router}
\label{sec:noc_router}

The NoC router (\texttt{router = noc}) is a simplified variant of the input-queued router. It does not support input or output speedup. Also, it does not support multi-cycle allocation.

@@

For the \texttt{islip}, \texttt{pim} and \texttt{select} allocators, allocation can be improved by performing multiple iterations of the algorithm; the number of iterations is controlled by the \texttt{alloc\_iters} parameter.

>>>>

\item[MECS] A topology based on ***. Currently it only supports single-flit packets.

@@

\item[alloc\_iters] For the \texttt{islip}, \texttt{pim} and \texttt{select} allocators, allocation can be improved by performing multiple iterations of the algorithm; this parameter controls the number of iterations to be performed for both switch and VC allocation.

@@

\item[sw\_alloc\_arb\_type] If the switch allocator is a separable input- or output-first allocator, this parameter selects the type of arbiter to use.

\item[sw\_alloc\_iters] If the switch allocator is of type \texttt{islip}, \texttt{pim} or \texttt{select}, this parameter controls how many allocation iterations should be performed. This overrides the global \texttt{alloc\_iters} parameter.

@@

\item[vc\_alloc\_arb\_type] If the VC allocator is a separable input- or output-first allocator, this parameter selects the type of arbiter to use.

\item[vc\_alloc\_iters] If the VC allocator is of type \texttt{islip}, \texttt{pim} or \texttt{select}, this parameter controls how many allocation iterations should be performed. This overrides the global \texttt{alloc\_iters} parameter.

@@

@@
